Fast approximate proposals for exact inference in stochastic kinetic models

### 2012-08-02 paper/paper.tex
Added bullet points to the paper

\title[This is an Example of Recto Running Head]{This is an Example of
an Article Title This is an Example of an Article Title}

@@

\begin{abstract}
The world will little note, nor long remember, what we say here, but
can never forget what they did here. It is for us, the living, rather
to be dedicated here to the unfinished work which they have, thus far,
so nobly carried out. It is rather for us to be here dedicated to the
great task remaining before us--that from these honored dead we take
increased devotion to that cause for which they here gave the last
full measures of devotion--that we here highly resolve that these dead
shall not have died in vain; that this nation shall have a new birth
of freedom; and that this government of the people, by the people, for
the people, shall not perish from the earth. The world will little
note.
\end{abstract}

@@

\section[]{Material Description of the Envelope\break Predominantly Model}

\subsection{Radial Distribution of Dust}

\subsection{An Example of Head two}
\subsubsection{An example of head three comparison with oxygen and~carbon~Miras}

% \begin{figure*}
% %  \centerline{\includegraphics[width=4.5in]{mouse.eps}}
%   \caption{An example of figure caption. An example of 
%   figure caption. An example of figure caption. An example of
%    figure caption. An example of figure caption.}
% \label{f:bigmouse}
% \end{figure*}

@@

>>>>

\title[Fast approximate proposals for exact inference in stochastic kinetic
models]{Fast approximate proposals for exact inference in stochastic kinetic
  models}

@@

\begin{abstract}
\begin{itemize}
\item Inference for MJP is difficult: non-linear likelihood, computational
  expensive, proposals expensive, analytically intractable likelihood
\item Data: Partially observed discrete, noisy time-course.
\item Existing work for likelihood evaluations: 
\begin{itemize}
\item Likelihood calculations
\begin{itemize}
\item Exact: Boys et al, slow, not noise
\item Approx SDE - Andy and Darren (with Noise)
\item Approx MC - Andy and Colin (no noise)
\item Approx LNA - Mark (no noise), Kolmo' (no noise, but check)
\end{itemize}
\item New:
\begin{itemize}
\item Approximate proposal mechanism based on the geometry of MC
\begin{itemize}
\item Overcome strong correlation structure which is standard with partially
  observed data
\item Fast proposals based on approximate geometry
\item Accept/reject with approximate model before trying exact model
\end{itemize}
\item Inference is exact
\item Including observational error
\item Time course measurements, unlike Mark's LNA
\end{itemize}
\item Examples:
\begin{itemize}
\item Immigration-death model: exact proposal compared with approximate proposal
  (no noise)
\item Aphid model: 3 blocks * 3 water treats * 3 nitro treats with Poisson error
\item Hidden states (counts), updated using standard method
\end{itemize}
\end{itemize}
\end{itemize}
\end{abstract}

@@

\begin{itemize}
\item Inference for MJP is difficult: non-linear likelihood, computational
  expensive, proposals expensive, analytically intractable likelihood
\item Data: Partially observed discrete, noisy time-course.
\item Existing work for likelihood evaluations: 
\begin{itemize}
\item Likelihood calculations
\begin{itemize}
\item Exact: Boys et al, slow, not noise
\item Approx SDE - Andy and Darren (with Noise)
\item Approx MC - Andy and Colin (no noise)
\item Approx LNA - Mark (no noise), Kolmo' (no noise, but check)
\end{itemize}
\end{itemize}
\item Novel stuff
\end{itemize}
Different from Mark's LNA paper:
\begin{itemize}
\item Analysis of impact of the approximate proposal scheme
\item Using Noise
\item Using delayed acceptance scheme so exact inference
\item Time course data
\item Using real data
\end{itemize}

\section{Methods}

\subsection{Stochastic kinetic models}

\subsection{Moment closure scheme}

\subsection{Approximate Riemannian Geometry}

\subsection{Delay acceptance scheme}

Key point: little overhead for approximate likelihood

\section{Example}

\subsection{Immigration-death}

\begin{itemize}
\item Comparison between approximate proposal and true proposal
\item Comparison between LNA and MC?
\item Three examples: increase correlation
\end{itemize}

\subsection{Independent time course}

Bimodal example??

\subsection{Aphid simulation study}

\section{Aphid real}

@@

\begin{itemize}
\item Use of geometry vital in tackling real problems
\item Could also use other approximation schemes such as the LNA??
\end{itemize}
